Group 5 Report

### 2022-08-02 Report/Group 5 report.Rmd
Note to include captions.

```{r, echo=FALSE, out.width="70%"}
knitr::include_graphics("Images/lagret_tekst.png") # må finne ut av hvordan vi deler disse bildene

@@

```{r, echo=FALSE, out.width="70%"}
knitr::include_graphics("Images/info_kreft.png")
```

```{r, echo=FALSE, out.width="100%"}
knitr::include_graphics("Images/regnskapssti.png")
```

>>>>

```{r, echo=FALSE, out.width="70%", fig.cap="Need caption"}
knitr::include_graphics("Images/lagret_tekst.png") # må finne ut av hvordan vi deler disse bildene

@@

```{r, echo=FALSE, out.width="70%", fig.cap="Need caption"}
knitr::include_graphics("Images/info_kreft.png")
```

```{r, echo=FALSE, out.width="100%", fig.cap="Need caption"}
knitr::include_graphics("Images/regnskapssti.png")
```
